A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-03-19 paper/theor-experiment.tex
updated figure and intro awa text

\vspace{-1em}
Compared to the Ferrario experiment in Section \ref{ferrario}, 
we increase the number of design variables and objectives by a factor of two.
The problem is also less predictable, due to the increased number of design variables
and nonlinear effects such as space charge, there is not a definite idea
before hand where the Pareto front will fall. This work is also meaningful in that
it will guide future operations at the AWA.

\begin{align}
\text{min}  \quad & \text{rms}_{x, s_1}, \quad \text{rms}_{x, s_2} \label{eq:awa:p1}\\
& \text{rms}_{s, s_1}, \quad \text{rms}_{s, s_2} \label{eq:awa:p2}\\
& \varepsilon_{x,s_1}, \quad \varepsilon_{x,s_2} \label{eq:awa:p3} \\
& dE \label{eq:awa:p4} \\
\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
\quad & \sigma_x = \sigma_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{linac}} =0 \label{eq:awa:lastdvar}
\end{align}

>>>>

\vspace{-1em}
We also chose this model to demonstrate the frameworks ability to tackle larger problems.
The number of design variables is eight, and the number of objectives is seven.
This problem is also less predictable, due to the high dimensionality 
and nonlinear effects such as space charge. There is not a definite idea
before hand where the Pareto front will fall. This work is also meaningful in that
it will guide future operations at the AWA.

\begin{align}
\text{min}  \quad & \text{rms}_{x, s_1}, \quad \text{rms}_{x, s_2} \label{eq:awa:p1}\\
& \text{rms}_{s, s_1}, \quad \text{rms}_{s, s_2} \label{eq:awa:p2}\\
& \varepsilon_{x,s_1}, \quad \varepsilon_{x,s_2} \label{eq:awa:p3} \\
& dE \label{eq:awa:p4} \\
\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
\quad & \sigma_x = \sigma_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{linac}} =0^\circ \label{eq:awa:lastdvar}
\end{align}
